A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-08-20 main.tex
4.1 - ugly placeholder true/false positive tables

\anna{add variable selection tables for these settings}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this work, we have reviewed the concept of population stratification and explicitly defined the environmental mechanism by which it may confound the genotype-phenotype relationship. We have provided a broad outline of existing methods for ameliorating the effects of these unobserved confounding influences. In addition, we have provided a thorough review of two popular approaches for correcting for population structure in genetic data: PC-Lasso and LMM-Lasso.

>>>>

\anna{Obviously these need to be formatted...}\\

\anna{True positive rates}
\begin{verbatim}
structureX    xi    method      `round(mean(value), 2)` `round(sd(value), 2)`
 1 1d_linear     0     lasso                         0.25                   0.05
 2 1d_linear     0     lasso_pca10                   0.23                   0.05
 3 1d_linear     0     lmm_ggmix                     0.25                   0.05
 4 1d_linear     0     lmm_lasso                     0.25                   0.05
 5 1d_linear     0     plmm_lasso                    0.25                   0.05
 6 1d_linear     0.8   lasso                         0.23                   0.05
 7 1d_linear     0.8   lasso_pca10                   0.28                   0.05
 8 1d_linear     0.8   lmm_ggmix                     0.28                   0.05
 9 1d_linear     0.8   lmm_lasso                     0.28                   0.05
10 1d_linear     0.8   plmm_lasso                    0.290                  0.05
11 indep_subpops 0     lasso                         0.23                   0.05
12 indep_subpops 0     lasso_pca10                   0.21                   0.05
13 indep_subpops 0     lmm_ggmix                     0.22                   0.05
14 indep_subpops 0     lmm_lasso                     0.23                   0.05
15 indep_subpops 0     plmm_lasso                    0.23                   0.05
16 indep_subpops 0.8   lasso                         0.25                   0.05
17 indep_subpops 0.8   lasso_pca10                   0.36                   0.06
18 indep_subpops 0.8   lmm_ggmix                     0.38                   0.06
19 indep_subpops 0.8   lmm_lasso                     0.38                   0.06
20 indep_subpops 0.8   plmm_lasso                    0.39                   0.06
21 other         0     lasso                         0.37                   0.06
22 other         0     lasso_pca10                   0.36                   0.06
23 other         0     lmm_ggmix                     0.4                    0.06
24 other         0     lmm_lasso                     0.4                    0.06
25 other         0     plmm_lasso                    0.41                   0.06
26 other         0.8   lasso                         0.290                  0.06
27 other         0.8   lasso_pca10                   0.47                   0.06
28 other         0.8   lmm_ggmix                     0.61                   0.06
29 other         0.8   lmm_lasso                     0.580                  0.06
30 other         0.8   plmm_lasso                    0.580                  0.06
\end{verbatim}

\anna{False positive rates}
\begin{verbatim}
   structureX    xi    method      `round(mean(value), 3)` `sd(value)`
 1 1d_linear     0     lasso                         0.038     0.00309
 2 1d_linear     0     lasso_pca10                   0.038     0.00317
 3 1d_linear     0     lmm_ggmix                     0.037     0.00343
 4 1d_linear     0     lmm_lasso                     0.037     0.00320
 5 1d_linear     0     plmm_lasso                    0.038     0.00311
 6 1d_linear     0.8   lasso                         0.039     0.00295
 7 1d_linear     0.8   lasso_pca10                   0.036     0.00307
 8 1d_linear     0.8   lmm_ggmix                     0.035     0.00328
 9 1d_linear     0.8   lmm_lasso                     0.035     0.00327
10 1d_linear     0.8   plmm_lasso                    0.036     0.00298
11 indep_subpops 0     lasso                         0.039     0.00301
12 indep_subpops 0     lasso_pca10                   0.039     0.00310
13 indep_subpops 0     lmm_ggmix                     0.038     0.00367
14 indep_subpops 0     lmm_lasso                     0.038     0.00315
15 indep_subpops 0     plmm_lasso                    0.039     0.00301
16 indep_subpops 0.8   lasso                         0.038     0.00307
17 indep_subpops 0.8   lasso_pca10                   0.032     0.00321
18 indep_subpops 0.8   lmm_ggmix                     0.03      0.00338
19 indep_subpops 0.8   lmm_lasso                     0.03      0.00338
20 indep_subpops 0.8   plmm_lasso                    0.031     0.00318
21 other         0     lasso                         0.031     0.00326
22 other         0     lasso_pca10                   0.031     0.00335
23 other         0     lmm_ggmix                     0.025     0.00451
24 other         0     lmm_lasso                     0.028     0.00358
25 other         0     plmm_lasso                    0.029     0.00335
26 other         0.8   lasso                         0.036     0.00300
27 other         0.8   lasso_pca10                   0.026     0.00338
28 other         0.8   lmm_ggmix                     0.016     0.00348
29 other         0.8   lmm_lasso                     0.02      0.00298
30 other         0.8   plmm_lasso                    0.021     0.00291
\end{verbatim}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\anna{this to change somewhat based on time/convergence results...}

In this work, we have reviewed the concept of population stratification and explicitly defined the environmental mechanism by which it may confound the genotype-phenotype relationship. We have provided a broad outline of existing methods for ameliorating the effects of these unobserved confounding influences. In addition, we have provided a thorough review of two popular approaches for correcting for population structure in genetic data: PC-Lasso and LMM-Lasso.
